Fair Queuing Aware Congestion Control

### 2022-09-29 tex/paper.tex
Add ecdfs for all bandwidths/delays combined

@@

\autoref{fig:no_fq} shows that if there is no fair queuing, Tonopah detects this correctly virtually always. 
If there is fair queuing with fq\_codel (\autoref{fig:fq_codel}) or fq (\autoref{fig:fq}), Tonopah detects this correctly very often but not in every case.

@@

@@

To evaluate Tonopah's performance under crosstraffic, we use iperf3 with the NewReno congestion control. We start iperf 4\,s before Tonopah so that it has time to saturate the link. 
\autoref{fig:no_fq_crosstraffic} and \autoref{fig:fq_crosstraffic} show that also in the presence of cross-traffic Tonpah's detection accuracy is virtually unchanged or even slightly better. We tried to use fq\_codel as in \autoref{fig:fq} but we encountered problems when using fq\_codel in combination with iperf3. Frequently, iperf3 would lose all packets, have a timeout after a couple of seconds and stop. Since we could not resolve this issue, we used fq instead of fq\_codel, for which this issue didn't occur.

>>>>

\begin{figure}[h]
\centering
\subfloat[\footnotesize pfifo]{\includegraphics[width=0.33\columnwidth]{{"../sample/plots/results_pfifo_new_tonopah"}.pdf}
\label{fig:ecdf_pfifo}}
\subfloat[\footnotesize fq\_codel]{\includegraphics[width=0.33\columnwidth]{{"../sample/plots/results_fq_codel_new_tonopah"}.pdf}
\label{fig:ecdf_fq_codel}}
\subfloat[\footnotesize fq]{\includegraphics[width=0.33\columnwidth]{{"../sample/plots/results_fq_new_tonopah"}.pdf}
\label{fig:ecdf_fq}}
\caption{Empirical cumulative distribution functions for detection of the abscence/presence of fair queuing.}
\label{fig:ecdf}
\end{figure}

@@

\autoref{fig:no_fq} shows that if there is no fair queuing, Tonopah detects this correctly virtually always. 
If there is fair queuing with fq\_codel (\autoref{fig:fq_codel}) or fq (\autoref{fig:fq}), Tonopah detects this correctly very often but not in every case. \autoref{fig:ecdf} shows the empirical cumulative distribution functions.

@@

\begin{figure}[h]
\centering
\subfloat[\footnotesize pfifo]{\includegraphics[width=0.33\columnwidth]{{"../sample/plots/results_pfifo_new_tonopah_iperf"}.pdf}
\label{fig:ecdf_crosstraffic_pfifo}}
\subfloat[\footnotesize fq]{\includegraphics[width=0.33\columnwidth]{{"../sample/plots/results_fq_new_tonopah_iperf"}.pdf}
\label{fig:ecdf_crosstraffic_fq}}
\caption{Empirical cumulative distribution functions for detection of the abscence/presence of fair queuing when there is cross-traffic.}
\label{fig:ecdf_crosstraffic}
\end{figure}

@@

To evaluate Tonopah's performance under cross-traffic, we use iperf3 with the NewReno congestion control. We start iperf 4\,s before Tonopah so that it has time to saturate the link. 
\autoref{fig:no_fq_crosstraffic} and \autoref{fig:fq_crosstraffic} show that also in the presence of cross-traffic Tonpah's detection accuracy is virtually unchanged or even slightly better. We tried to use fq\_codel as in \autoref{fig:fq} but we encountered problems when using fq\_codel in combination with iperf3. Frequently, iperf3 would lose all packets, have a timeout after a couple of seconds and stop. Since we could not resolve this issue, we used fq instead of fq\_codel, for which this issue didn't occur.

\autoref{fig:ecdf_crosstraffic} shows the empirical cumulative distribution functions when there is cross-traffic.
